---
title: "Chapter 3.4"
output: html_notebook
---

## Load data

```{r}
library(keras)

imdb <- dataset_imdb(num_words = 10000)
c(c(train_data, train_labels), c(test_data, test_labels)) %<-% imdb

str(train_data[[1]])
str(train_labels[[1]])
```

## Decode a review for fun

```{r}
word_index <- dataset_imdb_word_index()
reverse_word_index <- names(word_index)
names(reverse_word_index) <- word_index
decode_review <- sapply(train_data[[1]], function(index) {
  word <- if (index >= 3) reverse_word_index[[as.character(index - 3)]]
  if (!is.null(word)) word else "?"
})
decode_review
```

## Preprocess data

We're going to one-hot encode the training and test data. We will lose the order of the words in the review, but this is a simple example and we're treating the data as non-sequential, so the order does not matter. 

```{r}
vectorize_sequences <- function(sequences, dimension = 10000) {
  results <- matrix(0, nrow = length(sequences), ncol = dimension)
  for (i in 1:length(sequences)) {
    results[i, sequences[[i]]] <- 1
  }
  results
}

x_train <- vectorize_sequences(train_data)
x_test <- vectorize_sequences(test_data)

y_train <- as.numeric(train_labels)
y_test <- as.numeric(test_labels)
```

## Building the network

```{r}
model <- keras_model_sequential() %>%
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>%
  layer_dense(units = 16, activation = "relu") %>%
  layer_dense(units = 1, activation = "sigmoid")

model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

model
```

## Creating a validation (or dev) set

```{r}
val_indices <- 1:10000
x_val <- x_train[val_indices,]
partial_x_train <- x_train[-val_indices,]
y_val <- y_train[val_indices]
partial_y_train <- y_train[-val_indices]
```

## Train the model

```{r}
history <- model %>% fit(
  partial_x_train,
  partial_y_train,
  epochs = 20,
  batch_size = 512,
  validation_data = list(x_val, y_val)
)

plot(history)
```

## Retrain the model and stop at 4 epochs

```{r}
model <- keras_model_sequential() %>%
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>%
  layer_dense(units = 16, activation = "relu") %>%
  layer_dense(units = 1, activation = "sigmoid")

model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

model %>% fit(
  partial_x_train,
  partial_y_train,
  epochs = 4,
  batch_size = 512,
  validation_data = list(x_val, y_val)
)

results <- model %>% evaluate(x_test, y_test)
results
```

## Make predictions

```{r}
model %>% predict(x_test[1:10,])
```